%% Based on file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}
% possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\moderncvstyle{classic} % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green} % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\providecommand{\tightlist}{}
%\renewcommand{\familydefault}{\sfdefault} % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Fernando Luz}{}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
%\address{street}{zip, city}{country}
\email{prof.fernando.luz@gmail.com}

\phone[mobile]{+351 91 955 2453}

\homepage{tbd}
\social[linkedin]{fluz}
\social[github]{fluz}
\social[twitter][www.twitter.com/fluz]{fluz}

%\extrainfo{additional information}
%\photo[64pt][0.4pt]{lpenz.png}
%\quote{Some quote}

\begin{document}

\makecvtitle

\section{About me}

With over \textbf{16+ years} of experience in software development, I've
evolved from a proficient Software Engineer into an accomplished
\textbf{Engineering Manager}. My journey has encompassed a wide array of
projects and industries, from startups to oil and gas companies,
educational institutions, and research labs.

\vspace{1em}
As a \textbf{self-driven}, \textbf{quick learner}, and \textbf{top-notch
coder}, I've always been at the forefront of \textbf{solving complex
problems} and supporting my \textbf{development teams}. This journey
culminated in my transition to an Engineering Manager role.

\vspace{1em}
In this capacity, I thrive on maintaining \textbf{team collaboration} to
achieve project objectives. I firmly believe in the importance of
\textbf{knowledge sharing} and consistently promote \textbf{clear},
\textbf{high-quality coding} and \textbf{best practices}. My
transformation reflects my passion for talent development, driving
impactful projects, and contributing to organizational success at the
intersection of technology and engineering.


\clearpage

\section{Experience}


\cventry{2021 - Present}{}{}{}{}{As the Engineering Manager at Industries BU, I have overseen a %
comprehensive portfolio, which includes \textbf{Healthcare Experience %
Cloud (HEC)}, \textbf{Automated Notifications (AN)}, and \textbf{Agent %
Flows (AF)} products, along with the dedicated \textbf{QA} team. In this %
capacity, I've had the privilege of leading and mentoring a team of %
\textbf{13+ Individual Contributors}, ranging from entry-level %
professionals to team leads. %
 %
I've not only managed these \textbf{critical products} and teams but %
also \textbf{championed} a culture of innovation, %
\textbf{collaboration}, and \textbf{continuous improvement}. My role has %
been integral in driving our organization's commitment to delivering %
\textbf{high-quality} solutions and \textbf{fostering} a dynamic and %
\textbf{forward-thinking} work environment. %
}

\cventry{2021 - 2022}{}{}{}{}{Integrate a new team from the ground to create a new solution for %
banking financial services. %
 %
The tech stack in this project uses \textbf{Kotlin (BE)}, %
\textbf{SpringBoot}, \textbf{React (FE)}, \textbf{Redis}, %
\textbf{PostGres SQL}, \textbf{MongoDB}, \textbf{RabbitMQ}. %
}

\cventry{2018 - 2021}{}{}{}{}{Responsible to start the \textbf{ASML} project, where I contributed in %
\textbf{Variant Pattern} implementation at the robot component to be %
used in next lithography machine generation (EXE-5000), and currently %
I'm leading the Portugal team to expand unit tests quality using a %
framework based on \textbf{gtest}. I was one of the founders in the %
Meetup internal group in Altran PT. %
}

\cventry{2016 - 2018}{}{}{}{}{\textbf{Managed} the team responsible to implement new features in the %
\textbf{TMS (Technomar Maritime Simulator)}. \textbf{TMS} is a vessel %
maneuver simulator used in training activities. \textbf{Launched} the %
certification planning for \textbf{TMS} simulator by %
\href{https://www.dnvgl.com/}{DNV GL agency}, and the %
\textbf{collaborated} in the the core of hydrodynamic numerical model %
applied in a ``full bridge'' simulator. \textbf{Cultivated} good %
practices in software development process, such as \textbf{Scrum/Kanban} %
board, \textbf{TDD}, \textbf{Git} adoption and \textbf{mentored} meeting %
sessions to promote the homogenization of the knowledge of the team. %
}

\cventry{2008 - 2016}{}{}{}{}{My role in the TPN laboratory was to develop a set of applications with %
\textbf{High-Performance Computing}. The languages I use was %
\textbf{C++/C}, \textbf{Python}, \textbf{MPI/sockets} and \textbf{bash} %
in Linux and Windows environment. Other duties includes testing and %
validation of numerical simulations, optimization, implementation of %
parallel improvements and integration with other projects. I also worked %
in others several projects, including the first version of %
\textbf{vessel maneuver simulator} called \textbf{SMH}. This project was %
select as finalist of \textbf{ANP (National Petroleum Agency)} %
\href{http://www.anp.gov.br/pesquisa-desenvolvimento-inovacao/302-premio-anp-de-inovacao-tecnologica/edicoes-anteriores/888-premio-anp-de-inovacao-tecnologica-2016}{Prize %
Award for Technological Innovation in 2016}. %
}

\cventry{2011 - 2016}{}{}{}{}{Teaching-related responsibilities such as giving lectures, tutoring, %
manage homeworks, laboratory activities, exams preparation and grading. %
}


\clearpage

\section{Education}


\cventry{2015}{}{}{}{}{}

\cventry{2010}{}{}{}{}{}

\cventry{2006}{}{}{}{}{}



\section{Other courses}




\section{Languages}



\clearpage

\section{Random achievements and anecdotes}



\end{document}

% vim: ft=tex.jinja